\documentclass{res} 

\usepackage{cmbright}
\usepackage[top=0.5in, bottom=0in, left=0.5in, right=1.1in]{geometry}
\usepackage[T1]{fontenc}

\setlength{\textheight}{10in} % increase text height to fit on 1-page 

\begin{document}
	\name{ \huge{William Oursler}\\[24pt]}

	\address{
		Room 631D \\
		229 Vassar Street \\
		Cambridge, MA  02139
	}

	\address{
		\bf woursler.com \\
		woursler@mit.edu \\
		(541)-601-8295
	}

	\begin{resume}

		\vspace{-10pt}
		\section{Education}
			\begin{description}

				\item[Massachusetts Institute of Technology] \textit{2011 - 2015}

				Major: 6-2 (Electrical Engineering \& Computer Science)

				Notable Classes (Taken or Currently Enrolled):
				6.004 Computation Structures,
				6.002 Circuits \& Electronics,
				\\6.003 Signals and Systems,
				6.005 Elements of Software Construction,
				6.042 Mathematics for Computer Science,
				6.854 Advanced Algorithms,
				6.858 Computer Systems Security,
				6.832 Underactuated Robotics,
				\\6.115 Microcontrollers Lab,
				6.035 Computer Language Engineering,
				6.875 Cryptography and Cryptanalysis

			\end{description}

		\vspace{-20pt}
		\section{Experience}
			\vspace{-0.1in}

			\begin{tabbing}
				\hspace{2.3in}\= \hspace{2.6in}\= \kill % tabs
				{\bf Infrastructure Engineering Intern} \>Palantir Technologies, Palo Alto, CA \> \textit{Summer 2014}
				\\Designed and implemented a VM to support development of plugins for data integration tools, cutting plugin developers'
				\\iteration times in half while maintaining ease of build and release for my team.
			\end{tabbing}\vspace{-20pt}

			\begin{tabbing}
				\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
				{\bf Cyber-Auto Challenge}	\>Battelle, Columbus, OH	\> \textit{Summer 2013}

                \\Worked in an integrated team of students, scientists, government personnel, and auto industry engineers in a practicum-
                \\-based series of challenges oriented towards testing the cyber-security of CAN networks. 
			\end{tabbing}\vspace{-20pt}

			\begin{tabbing}
				\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
				{\bf Undergraduate Researcher}	\>Locomotion Lab (CSAIL), Cambridge, MA	\> \textit{Fall 2011 - Summer 2012}

				\\Implemented URDF support in Yobotics Simulation Construction Set (Java), learned various aspects of
				Control Design
				\\and Verification Theory.

			\end{tabbing}\vspace{-20pt}

			\begin{tabbing}
				\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
				{\bf Simmons Tech Member}	\>Simmons Hall, Cambridge, MA	\> \textit{Spring 2012 - Present}

				\\Part of a student committee tasked with managing dorm servers and information. Simmons Tech develops numerous
				\\services for residents. See http://github.com/simmons-tech/. I have personally worked on every repository listed.

			\end{tabbing}\vspace{-20pt}

			\begin{tabbing}
				\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
				{\bf Tech Consulting \& Web Design}	\>Rogue Valley Dermatology, Medford, OR	\> \textit{Fall 2007 - Present}

				\\Create and maintain a business webpage (rvderm.com), implemented a HIPPA compliant patient photo database, build
				\\and maintenance Office PCs and Network.

			\end{tabbing}\vspace{-20pt}

			\begin{tabbing}
				\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
				{\bf Volunteer Exhibit Interpreter}	\>ScienceWorks Museum, Ashland, OR	\> \textit{Fall 2007 - Spring 2011}
				\\Recognized for outstanding service and leadership. Assisted visitors with correct and safe use of exhibits, ensured exhibits
				\\ remained functional, and assisted instructors with demos, etc. during week-long camps. Recognized for outstanding
				\\ service and leadership.

			\end{tabbing}\vspace{-20pt}

		\section{Computer Skills}

			\begin{description}

				\item[C++] Implemented a kerneled Hough Transform module and GLUT GUI for a 3D scanner project (see woursler.com for details). Proficient with Visual Studio (5 years of experience).

				\item[Java] CSAIL UROP required work on the source of Yobotics Simulation Construction Set, written in Java. Coded many projects for the class 6.005, which is taught in Java, including a chat client.

				\item[Python] Numerous Simmons Tech projects, personal projects, etc. For instance, I use python to group news RSS feeds using kNN clustering based on n-grams cosine distance. Familiar with tkinter, numpy, and matplotlib among other modules. See github.com/zomega for a small sampling.

				\item[Web Development] Experience with HTML5 Development, including the use of LESS, CoffeeScript, and Django. See http://simmons-dev.mit.edu/dashboard for an ongoing project.

				\item[Git] Have used git for numerous projects, see http://github.com/zomega.

				\item[\LaTeX] This resume is typeset in \LaTeX. I also tend to \TeX \space math and CS psets.

				\item[Linux Terminal / Bash Scripting] Ubuntu Linux is my primary operating system, I help maintain our dorm server and the Xen VMs (Debian, Fedora, and Scientific Linux) running on it.

				\item[ROS (Robot Operating System)] Several personal projects, most recently a voice controlled hexapod.
				
				\item[Many Others] Vagrant, Xen, Expect, Apache Thrift, the occasional dabbling in Haskell/Prolog/FRACTRAN. 

			\end{description}
	\end{resume}
\end{document}
